### 2014-06-26 5/applications.tex
auto

In this chapter, some beneficial applications of the proposed models are presented,
  which demonstrate how the models' consistent sense of variance capability can help to break the vicious circle encountered in SAR speckle
filtering.
This chapter also shows how the MSE can then be 
applied in the additive and homoskedastic domain to evaluate SAR speckle filters, and further extends the concept to also evaluate
 POLSAR speckle filters.

@@

In a window of analysis, intensity dataset $X^I=\{x^I_1,...,x^I_n\}$ follows the exponential distribution given in Eqn. \ref{eqn:SAR Intensity PDF}. 
Assuming prior knowledge of it being homogeneous, thus having a single $\sigma$, the objective then is to estimate $\sigma$. 
This section shows how $\sigma$ can be estimated in the log-transformed domain.

It has already been proven that the log-transformed dataset $X^l=\log_2 \sigma$ follows a Fisher-Tippet distribution $pdf(x)= \ln 2 \frac{ 2^d }{ e^{2^d} }$, with $d=x-\mu$, and $\mu=2 \log_2 \sigma$. 
%***IVM: Hai can you clarify the \ln 2 \frac{ 2^d }{ e^{2^d} }, is that a base 2 in there? Maybe some brackets would help....
Thus the problem of estimating $\sigma$, casting into the log-transformed domain, equals to the problem of estimating $\mu$. 
The PDF given in Eqn. \ref{eqn:conditional_prob} can then be interpreted as
  the conditional probability of observing a single value of $x^l_i$ when the underlying coefficient equals $\mu$: %is estimated, $\sigma$ can also be estimated $\sigma=2^{ \frac{\mu}{2} }$.

@@

We have found that variance in the log-transformed domain is related to the standard Equivalent Number of Looks value.
Deriving from the results of \cite{Hoekman_1991_TGRS} and \cite{Xie_TGRS_2002_721}, the formula is given as:
$MSE = \frac{1}{(ENL - 0.5)ln^2(2)}$.
%An experiment is carried out to 
Fig. \ref{fig:verify_MSE_as_perf_index} demonstrates the relationship.
The use of iterative Fuzzy MLE estimations allows further suppression of speckle.
This is illustrated with ``tighter'' distance histograms and reducing MSE, as plotted in Fig. \ref{fig:Homogeneous_Area}

@@

In this section, a methodology to evaluate speckle filters over homogeneous areas in the log-transformed domain is 
illustrated. Under the condition of homogeneity, speckle filters are supposed to estimate with negligible bias.
Then the filters are traditionally compared by measuring their speckle suppression power using the ENL index.
Consequently, in the log-transformed domain, the first component of MSE evaluation (i.e. bias evaluation) is 
probably insignificant in comparison to the other components, namely, variance evaluation. 
%Subsection \ref{sec:homogeneous_theoretical} gives
The next section will give a theoretical justification for our methodology where variance 
methods of evaluation are shown to be mathematically related to the ENL index.
%The final subsection details how variance evaluation in the log-transformed domain to evaluate the levels of speckle 
over homogeneous areas.

@@

\begin{table}[h]
\centering
\begin{tabular}{r|c|c|c|c}
ENL & Var (Theory) & Var (Analysis) & Var (Observed) & $\hat{L}_{est} $ \\
\hline
2  & 1.3423 & 1.3876 & 1.3452 (0.0031) & 2.047 (0.0036)\\
3  & 0.8221 & 0.8326 & 0.8191 (4.2e-5) & 3.041 (0.0001)\\
4  & 0.5907 & 0.5947 & 0.5941 (0.0059) & 4.004 (0.0351)\\
5  & 0.4607 & 0.4625 & 0.4622 (0.0010) & 5.003 (0.0099)\\
6  & 0.3774 & 0.3784 & 0.3800 (0.0009) & 5.977 (0.0131)\\
7  & 0.3196 & 0.3202 & 0.3188 (0.0037) & 7.029 (0.0769)\\
8  & 0.2771 & 0.2775 & 0.2786 (0.0002) & 7.970 (0.0065)\\
9  & 0.2446 & 0.2449 & 0.2455 (0.0007) & 8.979 (0.0244)\\
10 & 0.2189 & 0.2191 & 0.2183 (0.0012) & 10.035 (0.0538)\\
11 & 0.1981 & 0.1982 & 0.1975 (0.0001) & 11.038 (0.0063)\\
12 & 0.1809 & 0.1809 & 0.1810 (0.0022) & 12.001 (0.1419)\\
13 & 0.1664 & 0.1665 & 0.1661 (0.0002) & 13.031 (0.0191)\\
14 & 0.1541 & 0.1542 & 0.1534 (0.0016) & 14.068 (0.1387)\\
15 & 0.1435 & 0.1435 & 0.1432 (0.0019) & 15.036 (0.1967)\\
16 & 0.1342 & 0.1343 & 0.1342 (0.0009) & 16.006 (0.0987)\\
17 & 0.1261 & 0.1261 & 0.1249 (0.0005) & 17.159 (0.0636)\\
18 & 0.1189 & 0.1189 & 0.1192 (0.0010) & 17.959 (0.1406)\\
19 & 0.1125 & 0.1125 & 0.1126 (0.0004) & 18.976 (0.0788)\\
20 & 0.1067 & 0.1067 & 0.1074 (0.0005) & 19.889 (0.0937)\\
21 & 0.1015 & 0.1015 & 0.1017 (0.0002) & 20.975 (0.0357)\\
22 & 0.0968 & 0.0968 & 0.0970 (0.0002) & 21.952 (0.0337)\\
23 & 0.0925 & 0.0925 & 0.0924 (0.0006) & 23.027 (0.1386)\\
24 & 0.0886 & 0.0886 & 0.0887 (0.0002) & 23.957 (0.0507)\\
25 & 0.0849 & 0.0849 & 0.0846 (0.0007) & 25.094 (0.1934)
\end{tabular}
\caption{ Speckle Suppression Power: ENL and Variance }
\label{tab:enl_in_log_domain}
\end{table}

@@

\begin{table}[h!]
\centering
\begin{tabular}{c|c|r|c|r}
Filter & Set & Log-Variance & $\hat{L}_{est}$ & Avg Intensity \\
\hline
none & 1 & 3.4149 (0.0003) & 1.1095 (5.8e-5) & 3.4795 (0.0029)\\
pde & 1 & 1.2674 (0.0014) & 2.1423 (0.0018) & 3.4806 (0.0029)\\
map & 1 & 1.2651 (0.0055) & 2.1454 (0.0072) & 3.1627 (0.0002)\\
lee & 1 & 0.4604 (0.0027) & 5.0206 (0.0268) & 3.4835 (0.0022)\\
kuan & 1 & 0.2979 (0.0024) & 7.4864 (0.0574) & 3.4748 (0.0054)\\
frost & 1 & 0.2852 (0.0012) & 7.7975 (0.0299) & 3.4799 (0.0027)\\
boxcar & 1 & 0.2513 (0.0011) & 8.7819 (0.0353) & 3.4799 (0.0027)\\
\hline
none & 2 & 3.4191 (0.0068) & 1.1088 (0.0012) & 9.4925 (0.0049)\\
pde & 2 & 1.6071 (0.0026) & 1.7952 (0.0021) & 9.4930 (0.0048)\\
map & 2 & 1.2646 (0.0023) & 2.1459 (0.0029) & 8.6091 (0.0162)\\
lee & 2 & 0.4653 (0.0026) & 4.9731 (0.0254) & 9.4936 (0.0080)\\
kuan & 2 & 0.2999 (0.0026) & 7.4391 (0.0602) & 9.4761 (0.0014)\\
frost & 2 & 0.2867 (0.0005) & 7.7595 (0.0128) & 9.4912 (0.0039)\\
boxcar & 2 & 0.2532 (0.0006) & 8.7203 (0.0193) & 9.4914 (0.0040)\\
\hline
none & 3 & 3.4203 (0.0187) & 1.1068 (0.0033) & 25.6234 (0.0389)\\
pde & 3 & 2.0353 (0.0021) & 1.5226 (0.0010) & 25.6236 (0.0389)\\
map & 3 & 1.2799 (0.0091) & 2.1263 (0.0116) & 23.2628 (0.0304)\\
lee & 3 & 0.4633 (2.4e-5) & 4.9926 (0.0002) & 25.6406 (0.0488)\\
kuan & 3 & 0.2964 (0.0010) & 7.5225 (0.0244) & 25.6112 (0.0226)\\
frost & 3 & 0.2862 (0.0008) & 7.7714 (0.0202) & 25.6263 (0.0409)\\
boxcar & 3 & 0.2529 (0.0005) & 8.7296 (0.0178) & 25.6261 (0.0407)
\end{tabular}
\caption{Performance of various filters over homogeneous areas}
\label{tab:homogeneous_performance_filters}
\end{table}

@@

Fig. \ref{fig:hetero_patterns_roc_auc} shows that feature preservation can be 
evaluated by examining the separability of the two background and target populations.
Figs. \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered} 
	allows visual evaluation of target and clutter histograms and their separability.
Quantitative evaluation of these separability is carried out by plotting the Receiver Operating Curve (ROC), 
in Figs. \ref{fig:hetero_patterns_roc_auc:roc_unfiltered} and \ref{fig:hetero_patterns_roc_auc:roc_kuan_filtered} 
respectively, and is measured by computing the Area Under these Curves (AUC).

@@

Detailed examination of Figs. \ref{fig:hetero_patterns_roc_auc} and \ref{fig:hetero_patterns_mse} 
	can help to explain how the MSE is related to the histograms' separation capability.
In pre-filtered images, shown in Figs. \ref{fig:hetero_patterns_roc_auc:hist_unfiltered} and 
\ref{fig:hetero_patterns_mse:unfiltered}, there is no bias error visible.
Then the separability of background and target populations depends only on the variance of the additive noise. 
This variance is visualized as the horizontal spread of the histograms.
Naturally, given a fixed location (i.e. expectation) of the two populations, the smaller the spread (i.e. variance) of these sample histograms, 
the better the separation capability.

In post-filtered images, shown in Figs. \ref{fig:hetero_patterns_roc_auc:hist_kuan_filtered} and 
\ref{fig:hetero_patterns_mse:kuan_filtered}, the situation is more complicated.
Here, besides the effect of the histogram spread, one also needs to take into account the bias error.
A closer examination of Fig. \ref{fig:hetero_patterns_mse:kuan_filtered} indicates that the output of the 
Kuan filter, and in fact the outputs of all other filters (which are not reproduced here due to space constraints), 
also introduce bias errors.
Specifically, the target (brighter) populations are always under-estimated and the clutter (darker) population are 
always over-estimated. This is probably due to the entropy reduction effect of the speckle filters.
Apparently, assuming that the variances are fixed, the lower these bias errors, the better the separation capability.

In SAR domain terminology, the general requirements of feature preservation for SAR speckle filters can be broken 
down into the requirements of radiometric preservation and speckle suppression.
In the log-transformed domain, these smaller requirements are equivalent to the bias and variance evaluation of 
statistical estimators respectively.
Overall, while the MSE index combines the measurements of bias and variance evaluation, 
	the feature preservation requirement, in the context of simple target and clutter scenes, can be measured by 
	the standard metric for target detectability: the Area Under the ROC Curve (AUC).

@@

\begin{table}[h!]
\centering
\begin{tabular}{c|r|c|c|r}
Pattern  & Filter  & AUC & $MSE_{true}$   & $MSE_{noise}$      \\% &85\%             &90\%\\
\hline
 point  &  unfiltered  &  0.741 (0.7e-3)  &  4.101 (1.3e-3)  &  2e-33 (4e-36) \\
 point  &  pde  &  0.789 (1.3e-3)  &  1.291 (5.1e-3)  &  1.817 (2.2e-3)\\
 point  &  map  &  0.813 (1.4e-3)  &  1.679 (2.2e-3)  &  2.183 (7.4e-3)\\
 point  &  frost  &  0.836 (1.8e-3)  &  0.536 (2.4e-3)  &  4.976 (6.9e-3)\\
 point  &  lee  &  0.857 (0.9e-3)  &  0.615 (3.1e-3)  &  3.189 (0.9e-3)\\
 point  &  boxcar  &  0.871 (1.5e-3)  &  0.471 (1.7e-3)  &  4.503 (5.4e-3)\\
 point  &  kuan  &  0.882 (1.1e-3)  &  0.448 (2.3e-3)  &  3.859 (3.4e-3)\\
\hline
 edge  &  unfiltered  &  0.738 (1.5e-4)  &  4.128 (9.0e-3)  &  2e-33 (1e-35)\\
 edge  &  pde  &  0.783 (0.6e-4)  &  1.409 (0.3e-3)  &  1.589 (0.4e-2)\\
 edge  &  map  &  0.830 (0.6e-4)  &  1.712 (3.5e-3)  &  2.184 (0.8e-2)\\
 edge  &  frost  &  0.841 (0.6e-4)  &  0.551 (0.1e-3)  &  5.035 (1.3e-2)\\
 edge  &  boxcar  &  0.871 (0.2e-4)  &  0.486 (0.2e-3)  &  4.560 (1.3e-2)\\
 edge  &  lee  &  0.872 (0.7e-4)  &  0.619 (2.2e-3)  &  3.233 (1.3e-2)\\
 edge  &  kuan  &  0.885 (0.4e-4)  &  0.471 (2.0e-3)  &  3.909 (1.1e-2)\\
\hline
 checker  &  unfiltered  &  0.738 (4.5e-4)  &  4.11 (7.8e-3)  &  2e-33 (5e-36)\\
 checker  &  pde  &  0.785 (6.2e-4)  &  1.445 (2.6e-3)  &  1.586 (2.4e-3)\\
 checker  &  map  &  0.836 (4.0e-4)  &  1.663 (1.1e-3)  &  2.213 (4.6e-3)\\
 checker  &  frost  &  0.855 (5.6e-4)  &  0.528 (2.2e-3)  &  4.965 (9.3e-3)\\
 checker  &  lee  &  0.879 (2.2e-4)  &  0.605 (1.7e-3)  &  3.229 (2.8e-3)\\
 checker  &  boxcar  &  0.883 (6.4e-4)  &  0.466 (2.4e-3)  &  4.493 (9.1e-3)\\
 checker  &  kuan  &  0.894 (4.2e-4)  &  0.453 (0.9e-3)  &  3.860 (9.5e-3)\\
\hline
 line  &  unfiltered  &  0.737 (1.1e-3)  &  4.129 (7.3e-3)  &  2e-33 (6e-36)\\
 line  &  pde  &  0.752 (1.2e-3)  &  1.339 (2.0e-3)  &  1.885 (3.7e-3)\\
 line  &  map  &  0.801 (1.6e-3)  &  1.706 (5.8e-3)  &  2.188 (3.5e-3)\\
 line  &  frost  &  0.831 (1.3e-3)  &  0.551 (1.1e-3)  &  5.023 (0.5e-3)\\
 line  &  lee  &  0.847 (1.5e-3)  &  0.623 (2.9e-3)  &  3.228 (4.8e-3)\\
 line  &  boxcar  &  0.865 (1.3e-3)  &  0.486 (0.9e-3)  &  4.549 (0.9e-3)\\
 line  &  kuan  &  0.874 (1.9e-3)  &  0.464 (1.9e-3)  &  3.897 (4.9e-3)\\
\hline
\end{tabular}

\caption{Lower MSE suggest better feature detection, measured by the AUC index}
\label{tab:mse_auc_in_log_domain}
\end{table}

\begin{table}[h!]
\centering
\begin{tabular}{c|c|c}
Pattern  & AUC - $MSE_{true}$  & AUC - $MSE_{benchmark}$  \\
\hline
edge & -0.8958 (1.5e-05) &   -0.9778  (1.6e-09) \\
point &     -0.9012   (1.1e-05)   &    -0.9816        (5.3e-10) \\
checker &   -0.9077     (7.3e-06)  &  -0.9829       (3.5e-10) \\
line &      -0.8223     (3.1e-04)  &   -0.9421       (4.8e-07) \\
\hline
\end{tabular}

\caption{The correlation between MSE and AUC evaluation criteria (inside the brackets are corresponding p-values)}
\label{tab:mse_auc_corr_coeff}
\end{table}

@@

\begin{table}[h!]
\centering
\begin{tabular}{r|r|c|c}
Pattern  & Filter  & $MSE_{true}$   & $MSE_{noise}$      \\% &85\%             &90\%\\
%\hline
%chu thap island	& none		& 4.1066	& 1.2e-33\\
%chu thap island	& pde			& 1.7966	& 1.0866\\
%chu thap island	& lee			& 0.5772	& 3.2378\\
%chu thap island	& frost		& 0.4701	& 4.8608\\
%chu thap island	& kuan		& 0.4196	& 3.7945\\
%chu thap island	& boxcar	& 0.4165	& 4.3952\\
%\hline
%ntu campus	& none		& 4.1231	& 8.7e-35\\
%ntu campus	& pde			& 3.6598	& 0.0733\\
%ntu campus	& lee			& 0.6335	& 3.2673\\
%ntu campus	& frost		& 0.5776	& 5.0569\\
%ntu campus	& boxcar	& 0.5136	& 4.5839\\
%ntu campus	& kuan		& 0.4910	& 3.9444\\
\hline
Vietnam rural	& none		& 4.1174	& 4e-35\\
Vietnam rural	& pde			& 3.8022	& 0.0368\\
Vietnam rural	& lee			& 0.4984	& 3.2555\\
Vietnam rural	& frost		& 0.3490	& 4.6856\\
Vietnam rural	& kuan		& 0.3396	& 3.6877\\
Vietnam rural	& boxcar	& 0.3107	& 4.2328\\
\hline
Hanoi suburb	& none		& 4.1321	& 4e-35\\
Hanoi suburb	& pde			& 3.8004	& 0.0391\\
Hanoi suburb	& lee			& 0.5261	& 3.2598\\
Hanoi suburb	& frost		& 0.3811	& 4.7427\\
Hanoi suburb	& kuan		& 0.3619	& 3.7270\\
Hanoi suburb	& boxcar	& 0.3395	& 4.2882\\
\hline
\end{tabular}

>>>>

In this chapter, some beneficial applications of the proposed models are presented,
  which demonstrate how the models' consistent sense of variance capability can help to break the vicious circle encountered in SAR speckle
filtering.
This chapter also shows how the Mean Squared Error (MSE) can then be 
applied in the additive and homoskedastic domain to evaluate SAR speckle filters, and further extends the concept to also evaluate
 POLSAR speckle filters.

@@

In a window of analysis, intensity dataset $X^I=\{x^I_1,...,x^I_n\}$ follows the exponential distribution given in Eqn. \ref{eqn:SAR Intensity PDF}. 
Assuming prior knowledge of it being homogeneous, thus having a single $\sigma$, the objective is to estimate $\sigma$. 
This section shows how $\sigma$ can be estimated in the log-transformed domain.

It has already been proven (see Eqn. \ref{eqn:SAR Log Intensity PDF}) that the log-transformed dataset $X^l=\log_2 \sigma$ follows a Fisher-Tippet distribution $pdf(x)= \ln 2 \frac{ 2^d }{ e^{2^d} }$, with $d=x-\mu$, and $\mu=2 \log_2 \sigma$. 
%***IVM: Hai can you clarify the \ln 2 \frac{ 2^d }{ e^{2^d} }, is that a base 2 in there? Maybe some brackets would help....
Thus the problem of estimating $\sigma$, casting into the log-transformed domain, equals to the problem of estimating $\mu$. 
The PDF given in Eqn. \ref{eqn:conditional_prob} can then be interpreted as
  the conditional probability of observing a single value of $x^l_i$ when the underlying coefficient equals $\mu$: %is estimated, $\sigma$ can also be estimated $\sigma=2^{ \frac{\mu}{2} }$.

@@

We have found that variance in the log-transformed domain is related to the standard Equivalent Number of Looks value.
Deriving from the results of \cite{Hoekman_1991_TGRS} and \cite{Xie_TGRS_2002_721}, the formula is given as:
$MSE = \frac{1}{(ENL - 0.5)ln^2(2)}$.
%An experiment is carried out to 
Fig. \ref{fig:verify_MSE_as_perf_index} demonstrates the relationship.
The use of iterative Fuzzy MLE estimations allows further suppression of speckle.
This is illustrated with ``tighter'' distance histograms and reducing Mean Squared Error (MSE), as plotted in Fig. \ref{fig:Homogeneous_Area}

@@

In this section, a methodology to evaluate speckle filters over homogeneous areas in the log-transformed domain is 
illustrated. Under the condition of homogeneity, speckle filters are supposed to estimate with negligible bias.
Then the filters are traditionally compared by measuring their speckle suppression power using the ENL index.
Consequently, in the log-transformed domain, the first component of MSE evaluation (i.e. bias evaluation) is 
probably insignificant in comparison to the other components, namely, variance evaluation. 
%Subsection \ref{sec:homogeneous_theoretical} gives
The next section will give a theoretical justification for our methodology where variance 
methods of evaluation are shown to be mathematically related to the ENL index.
%The final subsection details how variance evaluation in the log-transformed domain to evaluate the levels of speckle 
%over homogeneous areas.

@@

\begin{table}[h]
\centering
\caption{ Speckle Suppression Power: ENL and Variance }
\label{tab:enl_in_log_domain}
\begin{tabular}{r|c|c|c|c}
ENL & Var (Theory) & Var (Analysis) & Var (Observed) & $\hat{L}_{est} $ \\
\hline
2  & 1.3423 & 1.3876 & 1.3452 (0.0031) & 2.047 (0.0036)\\
3  & 0.8221 & 0.8326 & 0.8191 (4.2e-5) & 3.041 (0.0001)\\
4  & 0.5907 & 0.5947 & 0.5941 (0.0059) & 4.004 (0.0351)\\
5  & 0.4607 & 0.4625 & 0.4622 (0.0010) & 5.003 (0.0099)\\
6  & 0.3774 & 0.3784 & 0.3800 (0.0009) & 5.977 (0.0131)\\
7  & 0.3196 & 0.3202 & 0.3188 (0.0037) & 7.029 (0.0769)\\
8  & 0.2771 & 0.2775 & 0.2786 (0.0002) & 7.970 (0.0065)\\
9  & 0.2446 & 0.2449 & 0.2455 (0.0007) & 8.979 (0.0244)\\
10 & 0.2189 & 0.2191 & 0.2183 (0.0012) & 10.035 (0.0538)\\
11 & 0.1981 & 0.1982 & 0.1975 (0.0001) & 11.038 (0.0063)\\
12 & 0.1809 & 0.1809 & 0.1810 (0.0022) & 12.001 (0.1419)\\
13 & 0.1664 & 0.1665 & 0.1661 (0.0002) & 13.031 (0.0191)\\
14 & 0.1541 & 0.1542 & 0.1534 (0.0016) & 14.068 (0.1387)\\
15 & 0.1435 & 0.1435 & 0.1432 (0.0019) & 15.036 (0.1967)\\
16 & 0.1342 & 0.1343 & 0.1342 (0.0009) & 16.006 (0.0987)\\
17 & 0.1261 & 0.1261 & 0.1249 (0.0005) & 17.159 (0.0636)\\
18 & 0.1189 & 0.1189 & 0.1192 (0.0010) & 17.959 (0.1406)\\
19 & 0.1125 & 0.1125 & 0.1126 (0.0004) & 18.976 (0.0788)\\
20 & 0.1067 & 0.1067 & 0.1074 (0.0005) & 19.889 (0.0937)\\
21 & 0.1015 & 0.1015 & 0.1017 (0.0002) & 20.975 (0.0357)\\
22 & 0.0968 & 0.0968 & 0.0970 (0.0002) & 21.952 (0.0337)\\
23 & 0.0925 & 0.0925 & 0.0924 (0.0006) & 23.027 (0.1386)\\
24 & 0.0886 & 0.0886 & 0.0887 (0.0002) & 23.957 (0.0507)\\
25 & 0.0849 & 0.0849 & 0.0846 (0.0007) & 25.094 (0.1934)
\end{tabular}
\end{table}

@@

\begin{table}[h!]
\centering
\caption{Performance of various filters over homogeneous areas}
\label{tab:homogeneous_performance_filters}
\begin{tabular}{c|c|r|c|r}
Filter & Set & Log-Variance & $\hat{L}_{est}$ & Avg Intensity \\
\hline
none & 1 & 3.4149 (0.0003) & 1.1095 (5.8e-5) & 3.4795 (0.0029)\\
pde & 1 & 1.2674 (0.0014) & 2.1423 (0.0018) & 3.4806 (0.0029)\\
map & 1 & 1.2651 (0.0055) & 2.1454 (0.0072) & 3.1627 (0.0002)\\
lee & 1 & 0.4604 (0.0027) & 5.0206 (0.0268) & 3.4835 (0.0022)\\
kuan & 1 & 0.2979 (0.0024) & 7.4864 (0.0574) & 3.4748 (0.0054)\\
frost & 1 & 0.2852 (0.0012) & 7.7975 (0.0299) & 3.4799 (0.0027)\\
boxcar & 1 & 0.2513 (0.0011) & 8.7819 (0.0353) & 3.4799 (0.0027)\\
\hline
none & 2 & 3.4191 (0.0068) & 1.1088 (0.0012) & 9.4925 (0.0049)\\
pde & 2 & 1.6071 (0.0026) & 1.7952 (0.0021) & 9.4930 (0.0048)\\
map & 2 & 1.2646 (0.0023) & 2.1459 (0.0029) & 8.6091 (0.0162)\\
lee & 2 & 0.4653 (0.0026) & 4.9731 (0.0254) & 9.4936 (0.0080)\\
kuan & 2 & 0.2999 (0.0026) & 7.4391 (0.0602) & 9.4761 (0.0014)\\
frost & 2 & 0.2867 (0.0005) & 7.7595 (0.0128) & 9.4912 (0.0039)\\
boxcar & 2 & 0.2532 (0.0006) & 8.7203 (0.0193) & 9.4914 (0.0040)\\
\hline
none & 3 & 3.4203 (0.0187) & 1.1068 (0.0033) & 25.6234 (0.0389)\\
pde & 3 & 2.0353 (0.0021) & 1.5226 (0.0010) & 25.6236 (0.0389)\\
map & 3 & 1.2799 (0.0091) & 2.1263 (0.0116) & 23.2628 (0.0304)\\
lee & 3 & 0.4633 (2.4e-5) & 4.9926 (0.0002) & 25.6406 (0.0488)\\
kuan & 3 & 0.2964 (0.0010) & 7.5225 (0.0244) & 25.6112 (0.0226)\\
frost & 3 & 0.2862 (0.0008) & 7.7714 (0.0202) & 25.6263 (0.0409)\\
boxcar & 3 & 0.2529 (0.0005) & 8.7296 (0.0178) & 25.6261 (0.0407)
\end{tabular}
\end{table}

@@

Fig. \ref{fig:hetero_patterns_roc_auc} shows that feature preservation can be 
evaluated by examining the separability of the two background and target populations.
Figs. \subref*{fig:hetero_patterns_roc_auc:hist_unfiltered} and \subref*{fig:hetero_patterns_roc_auc:hist_kuan_filtered} 
	allows visual evaluation of target and clutter histograms and their separability.
Quantitative evaluation of these separability is carried out by plotting the Receiver Operating Curve (ROC), 
in Figs. \subref*{fig:hetero_patterns_roc_auc:roc_unfiltered} and \subref*{fig:hetero_patterns_roc_auc:roc_kuan_filtered} 
respectively, and is measured by computing the Area Under these Curves (AUC).

@@

Detailed examination of Figs. \ref{fig:hetero_patterns_roc_auc} and \ref{fig:hetero_patterns_mse} 
	can help to explain how the MSE is related to the histograms' separation capability.
In pre-filtered images, shown in Figs. \subref*{fig:hetero_patterns_roc_auc:hist_unfiltered} and 
\subref*{fig:hetero_patterns_mse:unfiltered}, there is no bias error visible.
Then the separability of background and target populations depends only on the variance of the additive noise. 
This variance is visualized as the horizontal spread of the histograms.
Naturally, given a fixed location (i.e. expectation) of the two populations, the smaller the spread (i.e. variance) of these sample histograms, 
the better the separation capability.

In post-filtered images, shown in Figs. \subref*{fig:hetero_patterns_roc_auc:hist_kuan_filtered} and 
\subref*{fig:hetero_patterns_mse:kuan_filtered}, the situation is more complicated.
Here, besides the effect of the histogram spread, one also needs to take into account the bias error.
A closer examination of Fig. \subref*{fig:hetero_patterns_mse:kuan_filtered} indicates that the output of the 
Kuan filter, and in fact the outputs of all other filters (which are not reproduced here due to space constraints), 
also introduce bias errors.
Specifically, the target (brighter) populations are always under-estimated and the clutter (darker) population are 
always over-estimated. This is probably due to the entropy reduction effect of the speckle filters.
Apparently, assuming that the variances are fixed, the lower these bias errors, the better the separation capability.

In SAR domain terminology, the general requirements of feature preservation for SAR speckle filters can be broken 
down into the requirements of radiometric preservation and speckle suppression.
In the log-transformed domain, these requirements are equivalent to the bias and variance evaluation of 
statistical estimators respectively.
Overall, while the MSE index combines the measurements of bias and variance evaluation, 
	the feature preservation requirement, in the context of simple target and clutter scenes, can be measured by 
	the standard metric for target detectability: the Area Under the ROC Curve (AUC).

@@

\begin{table}[h!]
\centering
\caption{Lower MSE suggest better feature detection, measured by the AUC index}
\label{tab:mse_auc_in_log_domain}

\begin{tabular}{c|r|c|c|r}
Pattern  & Filter  & AUC & $MSE_{true}$   & $MSE_{noise}$      \\% &85\%             &90\%\\
\hline
 point  &  unfiltered  &  0.741 (0.7e-3)  &  4.101 (1.3e-3)  &  2e-33 (4e-36) \\
 point  &  pde  &  0.789 (1.3e-3)  &  1.291 (5.1e-3)  &  1.817 (2.2e-3)\\
 point  &  map  &  0.813 (1.4e-3)  &  1.679 (2.2e-3)  &  2.183 (7.4e-3)\\
 point  &  frost  &  0.836 (1.8e-3)  &  0.536 (2.4e-3)  &  4.976 (6.9e-3)\\
 point  &  lee  &  0.857 (0.9e-3)  &  0.615 (3.1e-3)  &  3.189 (0.9e-3)\\
 point  &  boxcar  &  0.871 (1.5e-3)  &  0.471 (1.7e-3)  &  4.503 (5.4e-3)\\
 point  &  kuan  &  0.882 (1.1e-3)  &  0.448 (2.3e-3)  &  3.859 (3.4e-3)\\
\hline
 edge  &  unfiltered  &  0.738 (1.5e-4)  &  4.128 (9.0e-3)  &  2e-33 (1e-35)\\
 edge  &  pde  &  0.783 (0.6e-4)  &  1.409 (0.3e-3)  &  1.589 (0.4e-2)\\
 edge  &  map  &  0.830 (0.6e-4)  &  1.712 (3.5e-3)  &  2.184 (0.8e-2)\\
 edge  &  frost  &  0.841 (0.6e-4)  &  0.551 (0.1e-3)  &  5.035 (1.3e-2)\\
 edge  &  boxcar  &  0.871 (0.2e-4)  &  0.486 (0.2e-3)  &  4.560 (1.3e-2)\\
 edge  &  lee  &  0.872 (0.7e-4)  &  0.619 (2.2e-3)  &  3.233 (1.3e-2)\\
 edge  &  kuan  &  0.885 (0.4e-4)  &  0.471 (2.0e-3)  &  3.909 (1.1e-2)\\
\hline
 checker  &  unfiltered  &  0.738 (4.5e-4)  &  4.11 (7.8e-3)  &  2e-33 (5e-36)\\
 checker  &  pde  &  0.785 (6.2e-4)  &  1.445 (2.6e-3)  &  1.586 (2.4e-3)\\
 checker  &  map  &  0.836 (4.0e-4)  &  1.663 (1.1e-3)  &  2.213 (4.6e-3)\\
 checker  &  frost  &  0.855 (5.6e-4)  &  0.528 (2.2e-3)  &  4.965 (9.3e-3)\\
 checker  &  lee  &  0.879 (2.2e-4)  &  0.605 (1.7e-3)  &  3.229 (2.8e-3)\\
 checker  &  boxcar  &  0.883 (6.4e-4)  &  0.466 (2.4e-3)  &  4.493 (9.1e-3)\\
 checker  &  kuan  &  0.894 (4.2e-4)  &  0.453 (0.9e-3)  &  3.860 (9.5e-3)\\
\hline
 line  &  unfiltered  &  0.737 (1.1e-3)  &  4.129 (7.3e-3)  &  2e-33 (6e-36)\\
 line  &  pde  &  0.752 (1.2e-3)  &  1.339 (2.0e-3)  &  1.885 (3.7e-3)\\
 line  &  map  &  0.801 (1.6e-3)  &  1.706 (5.8e-3)  &  2.188 (3.5e-3)\\
 line  &  frost  &  0.831 (1.3e-3)  &  0.551 (1.1e-3)  &  5.023 (0.5e-3)\\
 line  &  lee  &  0.847 (1.5e-3)  &  0.623 (2.9e-3)  &  3.228 (4.8e-3)\\
 line  &  boxcar  &  0.865 (1.3e-3)  &  0.486 (0.9e-3)  &  4.549 (0.9e-3)\\
 line  &  kuan  &  0.874 (1.9e-3)  &  0.464 (1.9e-3)  &  3.897 (4.9e-3)\\
\hline
\end{tabular}

\end{table}

\begin{table}[h!]
\centering
\caption{The correlation between MSE and AUC evaluation criteria (inside the brackets are corresponding p-values)}
\label{tab:mse_auc_corr_coeff}
\begin{tabular}{c|c|c}
Pattern  & AUC - $MSE_{true}$  & AUC - $MSE_{benchmark}$  \\
\hline
edge & -0.8958 (1.5e-05) &   -0.9778  (1.6e-09) \\
point &     -0.9012   (1.1e-05)   &    -0.9816        (5.3e-10) \\
checker &   -0.9077     (7.3e-06)  &  -0.9829       (3.5e-10) \\
line &      -0.8223     (3.1e-04)  &   -0.9421       (4.8e-07) \\
\hline
\end{tabular}
\end{table}

@@

\begin{table}[h!]
\centering
\caption{If the best filters are the ones with smallest true MSE, then their observable noise-MSE are also the ones closest to the MSE of inherent noise}
\label{tab:mse_true_noise_log_domain}
\begin{tabular}{r|r|c|c}
Pattern  & Filter  & $MSE_{true}$   & $MSE_{noise}$      \\% &85\%             &90\%\\
%\hline
%chu thap island	& none		& 4.1066	& 1.2e-33\\
%chu thap island	& pde			& 1.7966	& 1.0866\\
%chu thap island	& lee			& 0.5772	& 3.2378\\
%chu thap island	& frost		& 0.4701	& 4.8608\\
%chu thap island	& kuan		& 0.4196	& 3.7945\\
%chu thap island	& boxcar	& 0.4165	& 4.3952\\
%\hline
%ntu campus	& none		& 4.1231	& 8.7e-35\\
%ntu campus	& pde			& 3.6598	& 0.0733\\
%ntu campus	& lee			& 0.6335	& 3.2673\\
%ntu campus	& frost		& 0.5776	& 5.0569\\
%ntu campus	& boxcar	& 0.5136	& 4.5839\\
%ntu campus	& kuan		& 0.4910	& 3.9444\\
\hline
Vietnam rural	& none		& 4.1174	& 4e-35\\
Vietnam rural	& pde			& 3.8022	& 0.0368\\
Vietnam rural	& lee			& 0.4984	& 3.2555\\
Vietnam rural	& frost		& 0.3490	& 4.6856\\
Vietnam rural	& kuan		& 0.3396	& 3.6877\\
Vietnam rural	& boxcar	& 0.3107	& 4.2328\\
\hline
Hanoi suburb	& none		& 4.1321	& 4e-35\\
Hanoi suburb	& pde			& 3.8004	& 0.0391\\
Hanoi suburb	& lee			& 0.5261	& 3.2598\\
Hanoi suburb	& frost		& 0.3811	& 4.7427\\
Hanoi suburb	& kuan		& 0.3619	& 3.7270\\
Hanoi suburb	& boxcar	& 0.3395	& 4.2882\\
\hline
\end{tabular}
\end{table}
